### 2015-02-23 fundamentals/impl.tex
cycamore listing now in rif order
consistent notation
made exclusive its own paragraph, closes #89

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
attach such constraints to its bids. Any potential resource transfer may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies.

@@

As of version 1.0, \Cycamore contains four facility archetypes, one region
archetype, and two institution archetypes. Short descriptions of these
functions can be found in Table \ref{tab:cycamore}.

@@

\begin{equation}
\begin{aligned}
 \min & \sum_{i=1}^{N}c_i y_i \\
 s.t. & \sum_{i=1}^{N}\phi_i y_i \ge \Phi \\
      & n_i \in [0,\infty) \:\: \forall i \in I, \:\: y_i \:\: \text{integer}
\end{aligned}
\end{equation}

>>>>

Suppliers then respond to the series of requests with a \textit{bid}. A bid
supplies a notion of the quantity and quality of a resource to match a
request. Suppliers may add an arbitrary number of constraints to accompany
bids. For example, an enriched \gls{UOX} supplier may be constrained by its current
inventory of natural uranium or its total capacity to provide enrichment (SWUs), and
attach such constraints to its bids.

Any potential resource transfer, i.e., a bid or a request, may be denoted as
\textit{exclusive}. An exclusive transfer must either be met fully or not at all
in order to support concepts such as the trading of individual reactor
assemblies. In combination with the notion of mutual requests, complex instances
of supply and demand are enabled.

@@

As of version 1.0, \Cycamore contains one region archetype, two institution
archetypes, and four facility archetypes. Short descriptions of these functions
can be found in Table \ref{tab:cycamore}.

@@

\begin{equation}
\begin{aligned}
 \min & \sum_{i=1}^{N}c_i y_i \\
 s.t. & \sum_{i=1}^{N}\phi_i y_i \ge \Phi \\
      & y_i \in [0,\infty) \:\: \forall i \in I, \:\: y_i \:\: \text{integer}
\end{aligned}
\end{equation}
